Non-kissing complexes and tau-tilting for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
minor changes

\begin{lemma}
\label{lem:exmBiclosedJI}
Let~$\sigma \in \strings^\pm(\bar Q)$ be a distinguishable string. Then the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
\end{lemma}

@@

\begin{theorem}
The following assertions are equivalent for a~$\Sigma \subseteq \distinguishableStrings^\pm(\bar Q)$:
\begin{enumerate}[(i)]
\item $\Sigma$ is pairwise non-friendly.
\item the set~$\ji(\Sigma) \eqdef \set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of an element in~$\NKL$.
\item $\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
\end{enumerate}
Thus, the canonical join complex of~$\NKL$ is isomorphic to the non-friendly complex~$\NFC$.
\end{theorem}

>>>>

\begin{lemma}
\label{lem:exmBiclosedJI}
For any distinguishable string~$\sigma \! \in \! \strings^\pm(\bar Q)$ the biclosed set~$\closure{\Sigma_\bottom(\sigma)}$ is join-irreducible in~$\Bicl{\bar Q}$.
\end{lemma}

@@

\begin{theorem}
The following assertions are equivalent for a~$\Sigma \subseteq \distinguishableStrings^\pm(\bar Q)$:
\begin{enumerate}[(i)]
\item the set~$\Sigma$ is pairwise non-friendly.
\item the set~$\ji(\Sigma) \eqdef \set{\ji(\sigma)}{\sigma \in \Sigma}$ is the canonical join-representation of an element in~$\NKL$.
\item the set~$\Sigma$ is the descent set of a non-kissing facet~$F \in \NKC$.
\end{enumerate}
Thus, the canonical join complex of~$\NKL$ is isomorphic to the non-friendly complex~$\NFC$.
\end{theorem}

### 2018-07-13 firstPaper/firstPaperShort/nonKissingComplex.tex
minor changes

\begin{table}
	\capstart{}
    \centerline{
    \begin{tabular}{|c|c|c|}
    \hline
    String modules on~$\bar Q$ &
    Walks on~$\bar Q\blossom$  &
    Reference
    \\ \hline \hline
    almost positive strings (Def.~\ref{def:stringsBands}) &
    bending walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    ?\footnotemark[1] &
    straight walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    \multiLinesBox{$P(v)$ and $P(v)[1]$ \\ $A=kQ/I$ and~$A[1]$ \\ ~} &
    \multiLinesBox{$v_\peak$ and $v_\deep$ \\ $F_\peak$ and~$F_\deep$ \\ (Exm.~\ref{example: Fdeep Fpeak} and Def.~\ref{def: deep walk})} &
    Lem.~\ref{lem:bijections-STTC-NKC}
    \\ \hline
    ?\footnotemark[2] &
    countercurrent order~$\prec_\alpha$ &
    ---
    \\ \hline
    $\tau$-compatibility (Def.~\ref{def: tau-compatibility}) &
    non-kissing (Def.~\ref{def: kissing}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting object (Def.~\ref{def: tau-rigid and stautilt}) &
    maximal non-kissing collection of walks &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting complex~$\tTC$ (Def.~\ref{def: stautilt complex}) &
    reduced non-kissing complex~$\RNKC$ (Def.~\ref{def: nKc}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm:mutationstautilts}~\cite{AdachiIyamaReiten})} &
    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    lattice of torsion classes &
    non-kissing lattice~$\NKL$ (Thm.~\ref{thm:lattice}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    bricks &
    \multiLinesBox{distinguishable strings (Def.~\ref{def:distinguishedSubstring})} &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    collections of pairwise Hom-orthogonal bricks &
    non-friendly complex (Def.~\ref{def: friendly}) &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    \multiLinesBox{bijection between indecomposable~$\tau$-rigid representations and bricks (Thm. 6.1 in~\cite{DemonetIyamaJasso})} &
    \multiLinesBox{bijection between non-kissing walks that are not peak walks and distinguishable strings (Prop.~\ref{prop:bijectionDistinguishableStringsWalks})} &
    \multiLinesBox{Conjectural \\ cf.~Prop.~\ref{prop:bijectionDistinguishableStringsJI}}[2cm]
    \\ \hline
    \multiLinesBox{Bongartz cocompletion of a~$\tau$-rigid indecomposable representation $N=M(\rho)$ whose associated brick is~$M(\sigma)$. Moreover $\sigma = \distinguishedWalk{\omega(\rho)}{F}$} &
    \multiLinesBox{$F=\eta\left(\closure{\Sigma_\bottom(\sigma)}\right)$, where $\sigma$ is a distinguishable string} &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    Bongartz completion &
    $\eta\left(\closure{\Sigma_\top(\sigma)}\right)$ &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    $\b{g}$-vector or index of a module (Def.~\ref{definition: g-vector of representation}) &
    $\b{g}$-vector of a walk (Def.~\ref{def: g-vectors for walks}) &
    Rem.~\ref{rem: g-vectors coincide}
    \\ \hline
    $\dim \Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$ (Sec.~\ref{subsec:tautilting}) &
    kissing number~$\kappa \big( \omega(\sigma), \omega(\sigma') \big)$ (Def.~\ref{def: kissing number}) &
    Rem.~\ref{rem:KNvsTau}
    \\ \hline
    \end{tabular}
    }
    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
    \label{table:dictionary}    
\end{table}

@@

\begin{remark}
The criterion of Proposition \ref{proposition: attract or dance and tau compatibility} for $\tau$-compatibility between string modules can be compared with a similar criterion obtained recently in \cite{CanakciPauksztelloSchroll} for the existence of extensions between two string modules.
The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Theorem IV.2.13]{AssemSimsonSkowronski}).
\end{remark}

@@

\begin{definition}
\label{def:increasingFlip}
\enlargethispage{.3cm}
If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
We denote by~$\ascents(F) \subseteq \strings^\pm(\bar Q)$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
%In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
\end{definition}

>>>>

\begin{table}
	\capstart{}
    \centerline{
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|c|c|c|}
    \hline
    String modules on~$\bar Q$ &
    Walks on~$\bar Q\blossom$  &
    Reference
    \\ \hline \hline
    almost positive strings (Def.~\ref{def:stringsBands}) &
    bending walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    ?\footnotemark[1] &
    straight walks (Def.~\ref{def:straightBended}) &
    Fig.~\ref{exm:exmBijectionStringsWalks1} \& \ref{fig:exmAuslanderReitenQuiver}
    \\ \hline
    \multiLinesBox{$P(v)$ and $P(v)[1]$ \\ $A=kQ/I$ and~$A[1]$ \\ ~} &
    \multiLinesBox{$v_\peak$ and $v_\deep$ \\ $F_\peak$ and~$F_\deep$ \\ (Exm.~\ref{example: Fdeep Fpeak} and Def.~\ref{def: deep walk})} &
    Lem.~\ref{lem:bijections-STTC-NKC}
    \\ \hline
    ?\footnotemark[2] &
    countercurrent order~$\prec_\alpha$ &
    ---
    \\ \hline
    $\tau$-compatibility (Def.~\ref{def: tau-compatibility}) &
    non-kissing (Def.~\ref{def: kissing}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting object (Def.~\ref{def: tau-rigid and stautilt}) &
    maximal non-kissing collection of walks &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    support~$\tau$-tilting complex~$\tTC$ (Def.~\ref{def: stautilt complex}) &
    reduced non-kissing complex~$\RNKC$ (Def.~\ref{def: nKc}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    \multiLinesBox{(left) mutation of support \\ $\tau$-tilting objects (Thm.~\ref{thm:mutationstautilts}~\cite{AdachiIyamaReiten})} &
    \multiLinesBox{(increasing) flip \\ (Prop.~\ref{prop:flip} and Def.~\ref{def:flip} \& \ref{def:increasingFlip})} &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    lattice of torsion classes &
    non-kissing lattice~$\NKL$ (Thm.~\ref{thm:lattice}) &
    Thm.~\ref{thm:nkc/sttiltc}
    \\ \hline
    bricks &
    \multiLinesBox{distinguishable strings (Def.~\ref{def:distinguishedSubstring})} &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    collections of pairwise Hom-orthogonal bricks &
    non-friendly complex (Def.~\ref{def: friendly}) &
    Prop.~\ref{prop:characterizationDistinguishableStrings}
    \\ \hline
    \multiLinesBox{bijection between indecomposable~$\tau$-rigid representations and bricks (Thm. 6.1 in~\cite{DemonetIyamaJasso})} &
    \multiLinesBox{bijection between non-kissing walks that are not peak walks and distinguishable strings (Prop.~\ref{prop:bijectionDistinguishableStringsWalks})} &
    \multiLinesBox{Conjectural \\ cf.~Prop.~\ref{prop:bijectionDistinguishableStringsJI}}[2cm]
    \\ \hline
    \multiLinesBox{Bongartz cocompletion of a~$\tau$-rigid indecomposable representation $N=M(\rho)$ whose associated brick is~$M(\sigma)$. Moreover $\sigma = \distinguishedWalk{\omega(\rho)}{F}$} &
    \multiLinesBox{$F=\eta\left(\closure{\Sigma_\bottom(\sigma)}\right)$, where $\sigma$ is a distinguishable string} &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    Bongartz completion &
    $\eta\left(\closure{\Sigma_\top(\sigma)}\right)$ &
    Rem.~\ref{rem: Bongartz}
    \\ \hline
    $\b{g}$-vector or index of a module (Def.~\ref{definition: g-vector of representation}) &
    $\b{g}$-vector of a walk (Def.~\ref{def: g-vectors for walks}) &
    Rem.~\ref{rem: g-vectors coincide}
    \\ \hline
    $\dim \Hom{A} \big( M(\sigma), \tau M(\sigma') \big)$ (Sec.~\ref{subsec:tautilting}) &
    kissing number~$\kappa \big( \omega(\sigma), \omega(\sigma') \big)$ (Def.~\ref{def: kissing number}) &
    Rem.~\ref{rem:KNvsTau}
    \\ \hline
    \end{tabular}
	\renewcommand{\arraystretch}{1}
    }
    \caption{Dictionary between algebraic notions on the support $\tau$-tilting complex and combinatorial notions on the non-kissing complex.}
    \label{table:dictionary}    
\end{table}

@@

\begin{remark}
The criterion of Proposition \ref{proposition: attract or dance and tau compatibility} for $\tau$-compatibility between string modules can be compared with a similar criterion obtained recently in \cite{CanakciPauksztelloSchroll} for the existence of extensions between two string modules.
The similarity between the two criteria is explained by the Auslander--Reiten formula asserting that $\Ext{}^1(N,M)$ is a quotient of the space $\Hom{}(M,\tau N)$ (see \cite[Thm.~IV.2.13]{AssemSimsonSkowronski}).
\end{remark}

@@

\begin{definition}
\label{def:increasingFlip}
\enlargethispage{.3cm}
If the common substring~$\sigma$ of~$\omega$ and~$\omega'$ is on top of~$\omega$ and at the bottom of~$\omega'$, then we say that the flip~$F \to F'$ is \defn{increasing} and that the common substring~$\sigma$ is an \defn{ascent} of~$F$ and a \defn{descent} of~$F'$.
We denote by~$\ascents(F) \subseteq \strings^\pm(\bar Q)$ and $\descents(F) \subseteq \strings^\pm(\bar Q)$ the sets of ascents and descents of~$F$ respectively.
%In the opposite situation, the flip is \defn{decreasing} and~$\sigma$ is a descent of~$F$ and an ascent of~$F'$.
Otherwise,~$\sigma$ is a descent of~$F$ and an ascent of~$F'$ and the flip is called \defn{decreasing}.
\end{definition}
